Polynomial phase estimation by least squares phase unwrapping

### 2013-12-16 paper.tex
minor

This section describes the results of Monte-Carlo simulations with the least squares unwrapping (LSU) estimator, the high order ambiguity function (HAF) estimator~\cite{Peleg_DPT_1995}, the product high order ambiguity function (PHAF) estimator~\cite{Barbarossa_PHAF_1998}, and the cubic phase function (CPF) estimator~\cite{Oshea_cpf_2004}.  Simulation are also performed with two recently proposed estimators that combine the HAF and CPF~\cite{Djurovic_haf_cpf_2012}.  The standard version of this estimator we refer to using the abreviation CPF-HAF~\cite[Sectoion~3]{Djurovic_haf_cpf_2012} and the product form of the estimator we abreviate by PCH~\cite[Section~5.A]{Djurovic_haf_cpf_2012}.  The CPF estimator only applies to polynomial phase signals of order $m=3$ and when the number of observations $N$ is odd.  In all simulations the unknown amplitude is $\rho = 1$ and $N = 199$.  The $X_1, \dots, X_N$ are pseudorandomly generated independent and identically distributed circularly symmetric complex Gaussian with variance $\expect\abs{X_1}^2 = \sigma_c^2$.  The corresponding signal to noise ratio (SNR) is $\rho^2 \sigma_c^{-2} = \sigma_c^{-2}$.  The number of replications of each Monte-Carlo experiment is $T = 2000$ to obtain estimates $\widehat{\mubf}_1, \dots, \widehat{\mubf}_T$ and the corresponding dealiased errors $\widehat{\lambdabf}_t = \dealias(\tilde{\mubf} - \widehat{\mubf}_t)$ are computed.  The sample mean square error (MSE) of the $k$th coefficient is computed according to $\tfrac{1}{T}\sum_{t=1}^T \widehat{\lambda}_{k,t}^2$ where $\widehat{\lambda}_{k,t}$ is the $k$th element of $\widehat{\lambdabf}_t$.  In all simulations four \emph{lag sets} are used for the PHAF and PCH estimators~\cite{Barbarossa_PHAF_1998,Djurovic_haf_cpf_2012} and the LSU estimator is approximated using the $K$-best method described in Section~\ref{sec:lattice-theory}.  The maximum number of branches allowed is $K=20N$.  The arithmetic complexity of the LSU estimator is $O(N^3\log N)$ in this case.

>>>>

This section describes the results of Monte-Carlo simulations with the least squares unwrapping (LSU) estimator, the high order ambiguity function (HAF) estimator~\cite{Peleg_DPT_1995}, the product high order ambiguity function (PHAF) estimator~\cite{Barbarossa_PHAF_1998}, and the cubic phase function (CPF) estimator~\cite{Oshea_cpf_2004}.  Simulation are also performed with two recently proposed estimators that combine the HAF and CPF~\cite{Djurovic_haf_cpf_2012}.  The standard version of this estimator we refer to using the abbreviation CPF-HAF~\cite[Section~3]{Djurovic_haf_cpf_2012} and the product form of the estimator we abbreviate by PCH~\cite[Section~5.A]{Djurovic_haf_cpf_2012}.  The CPF estimator only applies to polynomial phase signals of order $m=3$ and when the number of observations $N$ is odd.  In all simulations the unknown amplitude is $\rho = 1$ and $N = 199$.  The $X_1, \dots, X_N$ are pseudorandomly generated independent and identically distributed circularly symmetric complex Gaussian with variance $\expect\abs{X_1}^2 = \sigma_c^2$.  The corresponding signal to noise ratio (SNR) is $\rho^2 \sigma_c^{-2} = \sigma_c^{-2}$.  The number of replications of each Monte-Carlo experiment is $T = 2000$ to obtain estimates $\widehat{\mubf}_1, \dots, \widehat{\mubf}_T$ and the corresponding dealiased errors $\widehat{\lambdabf}_t = \dealias(\tilde{\mubf} - \widehat{\mubf}_t)$ are computed.  The sample mean square error (MSE) of the $k$th coefficient is computed according to $\tfrac{1}{T}\sum_{t=1}^T \widehat{\lambda}_{k,t}^2$ where $\widehat{\lambda}_{k,t}$ is the $k$th element of $\widehat{\lambdabf}_t$.  In all simulations four \emph{lag sets} are used for the PHAF and PCH estimators~\cite{Barbarossa_PHAF_1998,Djurovic_haf_cpf_2012} and the LSU estimator is approximated using the $K$-best method described in Section~\ref{sec:lattice-theory}.  The maximum number of branches allowed is $K=20N$.  The arithmetic complexity of the LSU estimator is $O(N^3\log N)$ in this case.
